A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-19 article/article.tex

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{plots/graph_embeddings_comparison_plausibility_check_0.png}

    \includegraphics[width=0.95\textwidth]{plots/graph_embeddings_comparison_plausibility_check_1.png}

    \includegraphics[width=0.95\textwidth]{plots/graph_embeddings_comparison_plausibility_check_2.png}

    \includegraphics[width=0.95\textwidth]{plots/graph_embeddings_comparison_plausibility_check_3.png}

    \includegraphics[width=0.95\textwidth]{plots/graph_embeddings_comparison_plausibility_check_4.png}
    \caption{Plausibility checks showing graph embedding comparisons. For randomly sampled scenarios, the most similar scenarios based on embedding distance (both Euclidean and cosine) are visualized, including comparisons between CARLA and Argoverse scenarios.}
    \label{fig:plausibility_checks}
\end{figure}
